Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-04-26 analysis/paper/paper.Rmd
Replace Nsub with N0...N180
This just makes it easier to follow the treatments and create the document

Use `kable` to generate the table because Pandoc > 2.0 is not in rocker/verse

library(bookdown)
library(knitr)
library(flextable)
library(ggpubr)
library(officer)
library(rice.awd.pests)
library(xtable)
```

@@

The split-plot treatment rates of nitrogen were N~0~ (no nitrogen supply), N~1~ (100 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) and N~2~ (120 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation).

@@

Split-plot N rates differed from the 2015 rates with only two nitrogen treatments, N~3~ (60 kg per ha as urea split into two applications) and N~4~ (180 kg per ha in three splits) being applied.

@@

In 2015 the incidence of tiller ShB remained low throughout the growing season only reaching 15% in 2015 in the N~2~, flooded treatment (Figure \@ref(fig:figure-1)). The nitrogen treatments, N~1~ and N~2~, were both significantly different when compared with the control N~0~ treatment. However, water management was not significantly different.

@@

In 2015 both the N~1~ and N~2~ treatments were significantly different than the control N~0~ treatment. However, the AWD water management was not significantly different from the FLD treatment.

@@

In 2015 both the N~1~ and N~2~ treatments were significantly different than the N~0~ treatment. However, the AWD water management was not significantly different from the FLD treatment.

@@

The changes to the inoculation methodology resulted in a much higher rate of infection in 2016, with the N~4~, flooded treatment reaching a maximum value of 98% incidence at the third observation (Figure \@ref(fig:figure-1)). The nitrogen treatment N~4~, was significantly different than the control N~3~ treatment. As in the 2015 study, water management did not significantly differ.

@@

In 2016 the N~4~ treatment was significantly different from the N~3~ treatment, with N~4~ severity being higher. The AWD water management, which was lower than FLD, was also significantly different.

@@

```{r N-management, tab.cap="Nitrogen application rates for 2015 and 2016. Five different nitrogen treatments were applied depending on the experiment. In the 2015 experiment three nitrogen rate treatments were applied: no N (N~0~), 100 kg per ha N (N~1~) and 180 kg per ha N (N~2~). In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N~3~) and 180 kg per ha N (N~4~). Treatments were applied in splits, basal, tillering and panicle initiation growth stages."}

N_rates <- xtable(N_rates) # the N_rates object is a tibble of data distributed with rice.awd.pests
N_rates <- xtable_to_flextable(x = N_rates, NA.string = "-")

N_rates <- flextable::display(
  N_rates,
  i = 1,
  col_key = "rowname",
  pattern = "{{val}}{{pow}}",
  part = "body",
  formatters = list(val ~ as.character("N"), pow ~ as.character("0")),
  fprops = list(pow = fp_text(
    vertical.align = "subscript", font.size = 8
  ))
)

N_rates <- flextable::display(
  N_rates,
  i = 2,
  col_key = "rowname",
  pattern = "{{val}}{{pow}}",
  part = "body",
  formatters = list(val ~ as.character("N"), pow ~ as.character("1")),
  fprops = list(pow = fp_text(
    vertical.align = "subscript", font.size = 8
  ))
)

N_rates <- flextable::display(
  N_rates,
  i = 3,
  col_key = "rowname",
  pattern = "{{val}}{{pow}}",
  part = "body",
  formatters = list(val ~ as.character("N"), pow ~ as.character("2")),
  fprops = list(pow = fp_text(
    vertical.align = "subscript", font.size = 8
  ))
)

N_rates <- flextable::display(
  N_rates,
  i = 4,
  col_key = "rowname",
  pattern = "{{val}}{{pow}}",
  part = "body",
  formatters = list(val ~ as.character("N"), pow ~ as.character("3")),
  fprops = list(pow = fp_text(
    vertical.align = "subscript", font.size = 8
  ))
)

N_rates <- flextable::display(
  N_rates,
  i = 5,
  col_key = "rowname",
  pattern = "{{val}}{{pow}}",
  part = "body",
  formatters = list(val ~ as.character("N"), pow ~ as.character("4")),
  fprops = list(pow = fp_text(
    vertical.align = "subscript", font.size = 8
  ))
)

N_rates <- add_header(N_rates,
                           Year = "Year",
                           Tillering = "Application Rate (kg/ha)")

N_rates <- merge_v(N_rates, part = "header")

N_rates <- autofit(N_rates)
N_rates

@@

```{r figure-1, fig.cap="Tiller sheath blight incidence progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years. Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD). Five different nitrogen treatments were applied depending on the experiment. In the 2015 experiment three nitrogen rate treatments were applied: no N (N~0~), 100 kg per ha N (N~1~) and 180 kg per ha N (N~2~). In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N~3~) and 180 kg per ha N (N~4~). Points represent the mean of four replications."}

@@

```{r figure-2, fig.cap="Tiller sheath blight severity progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years. Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD). Five different nitrogen treatments were applied depending on the experiment. In the 2015 experiment three nitrogen rate treatments were applied: no N (N~0~), 100 kg per ha N (N~1~) and 180 kg per ha N (N~2~). In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N~3~) and 180 kg per ha N (N~4~). Points represent the mean of four replications."}

@@

```{r figure-3, fig.cap="Leaf sheath blight severity progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season in both years. Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD). Five different nitrogen treatments were applied depending on the experiment. In the 2015 experiment three nitrogen rate treatments were applied: no N (N~0~), 100 kg per ha N (N~1~) and 180 kg per ha N (N~2~). In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N~3~) and 180 kg per ha N (N~4~). Points represent the mean of four replications."}

>>>>

library(bookdown)
library(kableExtra)
library(knitr)
library(ggpubr)
library(rice.awd.pests)
```

@@

The split-plot treatment rates of nitrogen were N0 (no nitrogen supply), N100 (100 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) and N120 (120 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation).

@@

Split-plot N rates differed from the 2015 rates with only two nitrogen treatments, N60 (60 kg per ha as urea split into two applications) and N180 (180 kg per ha in three splits) being applied.

@@

In 2015 the incidence of tiller ShB remained low throughout the growing season only reaching 15% in 2015 in the N120, flooded treatment (Figure \@ref(fig:figure-1)). The nitrogen treatments, N100 and N120, were both significantly different when compared with the control N0 treatment. However, water management was not significantly different.

@@

In 2015 both the N100 and N120 treatments were significantly different than the control N0 treatment. However, the AWD water management was not significantly different from the FLD treatment.

@@

In 2015 both the N100 and N120 treatments were significantly different than the N0 treatment. However, the AWD water management was not significantly different from the FLD treatment.

@@

The changes to the inoculation methodology resulted in a higher rate of infection in 2016, with the N180, flooded treatment reaching a maximum value of 98% incidence at the third observation (Figure \@ref(fig:figure-1)). The nitrogen treatment N180, was significantly different than the control N60 treatment. As in the 2015 study, water management did not significantly differ.

@@

In 2016 the N180 treatment was significantly different from the N60 treatment, with N180 severity being higher. The AWD water management, which was lower than FLD, was also significantly different.

@@

```{r table-1, tab.cap="Nitrogen application rates for 2015 and 2016. Five different nitrogen treatments were applied depending on the experiment. In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120). In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180). Treatments were applied in splits, basal, tillering and panicle initiation growth stages."}
kable(N_rates)

@@

```{r figure-1, fig.cap="Tiller sheath blight incidence progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years. Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD). Five different nitrogen treatments were applied depending on the experiment. In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120). In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180). Points represent the mean of four replications."}

@@

```{r figure-2, fig.cap="Tiller sheath blight severity progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years. Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD). Five different nitrogen treatments were applied depending on the experiment. In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120). In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180). Points represent the mean of four replications."}

@@

```{r figure-3, fig.cap="Leaf sheath blight severity progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season in both years. Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD). Five different nitrogen treatments were applied depending on the experiment. In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120). In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180). Points represent the mean of four replications."}
